---
title: "Standard Curves for qPCR manuscript"
author: "Emily Roggenkamp"
date: "10/27/2022"
output: html_document
---
## Data Wrangling
Input Data - in csv format with log10(concentrations) and Cq values
```{r, message = FALSE, include = FALSE}
setwd("/path/")
```
```{r}
stdcurve <- read.csv("Plate_3_std_curve.csv", header = TRUE)
spore <- read.csv("spore_curve.csv", header = TRUE)
supcurve <- read.csv("standard_curve_blue.csv", header = TRUE)
supspore <- read.csv("spore_curve_blue.csv", header = TRUE)
allcurve <- read.csv("allcurves.csv", header = TRUE)
```
Make log scaling
```{r, message = FALSE}
stdcurve$log <- log(stdcurve$fg, base = 10)
allcurve$log <- log(allcurve$fg, base = 10)
stdcurve
```
## Load Packages
```{r, message = FALSE}
library(ggplot2)
library(ggpubr)
```
## Change significant digits for regression equation
Change lines 13-14 to the number of significant digits for the equation and line 9 for R squared. I used 3 for equation and 4 for R squared
```{r, message = FALSE}
trace(ggpubr:::.stat_lm, edit = TRUE)
 #untrace(ggpubr:::.stat_lm)
```
# DNA concentration regression
## Multiplex Mix
### Figure 2
```{r, message = FALSE, warning = FALSE}
stdcurve_plot <- ggplot(data = stdcurve, aes(x = log, y = Cq), add = "reg.line") +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, color='black') +
  stat_regline_equation(label.x = 5, label.y = 37.5) +
  stat_cor(aes(label = paste(..rr.label..)), label.x = 5, label.y = 40, r.digits=4) +
  scale_x_continuous(name = "Log10(Genomic DNA concentration fg)", breaks = c(1,2,3,4,5,6,7)) +
  scale_y_continuous(name = "Cq", limits = c(15, 40), n.breaks = 6) +
  theme_classic2() +
  ggtitle("Standard Curve",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

stdcurve_plot
```

## Non-Multiplex Mix
### Supplemental Figure 2
```{r, message = FALSE, warning = FALSE}
stdcurve_plot_sup <- ggplot(data = supcurve, aes(x = log, y = Cq), add = "reg.line") +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, color='black') +
  stat_regline_equation(label.x = 5, label.y = 37.5) +
  stat_cor(aes(label = paste(..rr.label..)), label.x = 5, label.y = 40, r.digits=4) +
  scale_x_continuous(name = "Log10(Genomic DNA concentration fg)", breaks = c(1,2,3,4,5,6,7)) +
  scale_y_continuous(name = "Cq", limits = c(15, 40), n.breaks = 6) +
  theme_classic2() +
  ggtitle("Standard Curve Non-Multiplex",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

stdcurve_plot_sup
```

# Spore Concentration Regression
## Multiplex Mix
### Figure 3
```{r, message = FALSE, warning = FALSE}
spore_plot <- ggplot(data = spore, aes(x = spore, y = Cq), add = "reg.line") +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, color='black') +
  stat_regline_equation(label.x = 4, label.y = 42.5) +
  stat_cor(aes(label = paste(..rr.label..)), label.x = 4, label.y = 45, r.digits=4) +
  scale_x_continuous(name = "Log10(Number of Spores)", breaks = c(1,2,3,4,5,6)) +
  scale_y_continuous(name = "Cq", limits = c(15, 45), n.breaks = 7) +
  theme_classic2() +
  ggtitle("Spore Standard Curve",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

spore_plot
```

## Non-Multiplex Mix
### Supplemental Figure 3
```{r, message = FALSE, warning = FALSE}
spore_plot_sup <- ggplot(data = supspore, aes(x = spore, y = Cq), add = "reg.line") +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, color='black') +
  stat_regline_equation(label.x = 4, label.y = 42.5) +
  stat_cor(aes(label = paste(..rr.label..)), label.x = 4, label.y = 45, r.digits=4) +
  scale_x_continuous(name = "Log10(Number of Spores)", n.breaks = 6) +
  scale_y_continuous(name = "Cq", limits = c(15, 45), n.breaks = 7) +
  theme_classic2() +
  ggtitle("Spore Standard Curve Non-Multiplex",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

spore_plot_sup
```

## Transferability Standard Curves

### Supplemental Figure 4

```{r, message = FALSE, warning = FALSE}
allcurve_plot <- ggplot(data = allcurve, aes(x = log, y = Cq, color = Lab) ) +
  geom_point(aes(color = Lab)) +
  geom_smooth(aes(color = Lab), method=lm, se=FALSE) +
  stat_regline_equation(aes(label=paste(..eq.label..,..rr.label.., sep = "~~~")), label.x.npc = "left",
                        label.y.npc = 0.4,formula = y ~ x, size = 3) +
  scale_x_continuous(name = "Log10(Genomic DNA concentration fg)", breaks = c(1,2,3,4,5,6,7)) +
  scale_y_continuous(name = "Cq", limits = c(15, 40), n.breaks = 6) +
  labs(color = "Lab") +
  theme_classic2() +
  ggtitle("Multi-Lab Standard Curves",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"), legend.position = "right") +
  scale_color_discrete(breaks = c("MSU", "1", "2", "3", "4", "5"))
allcurve_plot

```

## Save Plots for Publication
```{r, message = FALSE}
#ggsave(filename = "std_curve.png", plot = stdcurve_plot, device = "png", path = "/path/", width = 100, height = 100, units="mm", dpi = 600)

```
